Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-23 Arxiv/main.tex
update proof

In Bayesian Inference data analysis, some algorithms have been studied and mechanisms proposed corresponded to maintain their differential privacy. There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zheng2015differential} and \citet{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential},  \citet{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself. The third topic where our work focus on is still very new.

@@

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ (or $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System), $\hexpmech$ is $(\epsilon, \delta) -$differentially private.

@@

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

@@

\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

>>>>

In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zheng2015differential} and \citet{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential},  \citet{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy. The third topic where our work focus on is still very new.

@@

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2}) -$differentially private. (or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)

@@

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

@@

\noindent \textbf{$(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2})-$Differential Privacy of $\hexpmech$}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2})$-differential privacy.
\end{lem}
